---
title: "ODD Sales Assignment"
author: "Omer Elmasri"
date: "31.10.2018"
output: html_document
---
## November 2017  Sales Analysis 


### Make library active
```{r message = FALSE}
library(dplyr)
library(tidyverse)
library(scales)
library(readxl)
```

## From Raw to Civilized Data

### Find the data
  First, car sales excel for November 2017 is downloaded from "Otomotiv Distibütörleri Derneği" website. [webSite](http://www.odd.org.tr/web_2837_1/neuralnetwork.aspx?type=36). 
  File is renamed to "odd_retail_sales_2017_11.xlsx"" and uploaded to github [github link](https://github.com/MEF-BDA503/pj18-elmasriomer) 

### Download Raw Data
  Below the excel file is downloaded from github to a local data frame (raw_data) and refined for analysis
```{r}
tmp<-tempfile(fileext=".xlsx")
download.file("https://github.com/MEF-BDA503/pj18-elmasriomer/blob/master/odd_retail_sales_2017_11.XLSX?raw=true",destfile=tmp,mode="wb")
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
file.remove(tmp)
raw_data <- raw_data %>% slice(-c(46,47))
head(raw_data)
```

### Civilize Data
In order to make easy to read, we have named column names. 
```{r}
#column names for raw data
colnames(raw_data) <- c("brand_name","auto_dom","auto_imp","auto_total","comm_dom","comm_imp","comm_total","total_dom","total_imp","total_total")
#replace NA values with 0 and add year/month cols
car_data_nov_17 <- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.)))%>% mutate(year=2017,month=11)
print(car_data_nov_17,width=Inf)
```

### Saving Data to Local Documentary
```{r}
saveRDS(car_data_nov_17,file="C:/Users/USER/Documents/Data_Analytics/odd_retail_sales_2017_11.rds")
```

### Analysis with Data 
##### Default code to see the both of automobile and commercial vehicle sales over 0 valuewith brandnames as descending in the total sales
```{r}
car_data_nov_17 %>% 
  filter(auto_total > 0 & comm_total > 0) %>%
  select(brand_name,total_total) %>%
  arrange(desc(total_total))

```

##### Total sales of both of automobile and commercial vehicles where these are over 0 value and percentage by brand name
```{r}
car_data_nov_17 %>% 
  filter(auto_total > 0 & comm_total > 0) %>%
  select(brand_name,total_total) %>%
  arrange(desc(total_total))  %>%
  mutate(percentage = percent(total_total/sum(total_total))) %>% slice(1:10)
```


##### Now, I would like to see a list which total sales is greater than average total sales value in all brands.
```{r}
car_data_nov_17 %>% 
  select(brand_name, auto_total, comm_total, total_total) %>%
  mutate(average_total=mean(total_total)) %>%  
  filter(total_total > average_total)  %>%
  arrange(desc(total_total)) 
```

##### Also I would like to see a vehicle list which their brand names start with "M" letter with total of automotive and commercial sales

```{r}
  filtered_df <- car_data_nov_17 %>% dplyr::filter(substr(brand_name,1,1) == "M")
  select(filtered_df, brand_name, total_total) %>%
  arrange(desc(total_total))  %>%
  print(filtered_df)

```

  