---
title: "ODD Sales Assignment"
author: "Omer Elmasri"
date: "31.10.2018"
output: html_document
---
## November 2017  Sales Analysis 


### Make library active
```{r message = FALSE}
library(dplyr)
library(tidyverse)
library(scales)
library(readxl)
```

## From Raw to Civilized Data

### Find the data
  First, car sales excel for November 2017 is downloaded from "Otomotiv Distibütörleri Derneði" website. [webSite](http://www.odd.org.tr/web_2837_1/neuralnetwork.aspx?type=36). 
  File is renamed to "odd_retail_sales_2017_11.xlsx"" and uploaded to github [github link](https://github.com/MEF-BDA503/pj18-elmasriomer) 

### Download Raw Data
  Below the excel file is downloaded from github to a local data frame (raw_data) and refined for analysis
```{r}
tmp<-tempfile(fileext=".xlsx")
download.file("https://github.com/MEF-BDA503/pj18-elmasriomer/blob/master/odd_retail_sales_2017_11.XLSX?raw=true",destfile=tmp,mode="wb")
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
file.remove(tmp)
raw_data <- raw_data %>% slice(-c(46,47))
head(raw_data)
```

# A tibble: 6 x 10
  brand_name   auto_dom auto_imp auto_total comm_dom comm_imp comm_total total_dom total_imp total_total
  <chr>           <dbl>    <dbl>      <dbl>    <dbl>    <dbl>      <dbl>     <dbl>     <dbl>       <dbl>
1 ALFA ROMEO         NA       53         53       NA       NA          0         0        53          53
2 ASTON MARTIN       NA        2          2       NA       NA          0         0         2           2
3 AUDI               NA     3189       3189       NA       NA          0         0      3189        3189
4 BENTLEY            NA        2          2       NA       NA          0         0         2           2
5 BMW                NA     4611       4611       NA       NA          0         0      4611        4611
6 CHERY              NA        0          0       NA       NA          0         0         0           0


### Civilize Data
In order to make easy to read, we have named column names. 
```{r}
#column names for raw data
colnames(raw_data) <- c("brand_name","auto_dom","auto_imp","auto_total","comm_dom","comm_imp","comm_total","total_dom","total_imp","total_total")
#replace NA values with 0 and add year/month cols
car_data_nov_17 <- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.)))%>% mutate(year=2017,month=11)
print(car_data_nov_17,width=Inf)
```

# A tibble: 45 x 12
   brand_name   auto_dom auto_imp auto_total comm_dom comm_imp comm_total total_dom total_imp total_total  year month
   <chr>           <dbl>    <dbl>      <dbl>    <dbl>    <dbl>      <dbl>     <dbl>     <dbl>       <dbl> <dbl> <dbl>
 1 ALFA ROMEO          0       53         53        0        0          0         0        53          53  2017    11
 2 ASTON MARTIN        0        2          2        0        0          0         0         2           2  2017    11
 3 AUDI                0     3189       3189        0        0          0         0      3189        3189  2017    11
 4 BENTLEY             0        2          2        0        0          0         0         2           2  2017    11
 5 BMW                 0     4611       4611        0        0          0         0      4611        4611  2017    11
 6 CHERY               0        0          0        0        0          0         0         0           0  2017    11
 7 CITROEN             0     2017       2017      274      711        985       274      2728        3002  2017    11
 8 DACIA               0     4745       4745        0      747        747         0      5492        5492  2017    11
 9 DS                  0       42         42        0        0          0         0        42          42  2017    11
10 FERRARI             0        2          2        0        0          0         0         2           2  2017    11
# ... with 35 more rows

### Saving Data to Local Documentary
```{r}
saveRDS(car_data_nov_17,file="C:/Users/USER/Desktop/Data_Analytics/odd_retail_sales_2017_11.rds")
```

### Analysis with Data 
##### Default code to see the both of automobile and commercial vehicle sales over 0 valuewith brandnames as descending in the total sales
```{r}
car_data_nov_17 %>% 
  filter(auto_total > 0 & comm_total > 0) %>%
  select(brand_name,total_total) %>%
  arrange(desc(total_total))

```

# A tibble: 12 x 2
   brand_name    total_total
   <chr>               <dbl>
 1 FIAT                13229
 2 RENAULT             12760
 3 FORD                12500
 4 MERCEDES-BENZ        6933
 5 HYUNDAI              5829
 6 DACIA                5492
 7 NISSAN               4429
 8 PEUGEOT              4220
 9 CITROEN              3002
10 KIA                  2789
11 MITSUBISHI            463
12 SSANGYONG              77

##### Total sales of both of automobile and commercial vehicles where these are over 0 value and percentage by brand name
```{r}
car_data_nov_17 %>% 
  filter(auto_total > 0 & comm_total > 0) %>%
  select(brand_name,total_total) %>%
  arrange(desc(total_total))  %>%
  mutate(percentage = percent(total_total/sum(total_total)))
```
# A tibble: 12 x 3
   brand_name    total_total percentage
   <chr>               <dbl> <chr>     
 1 FIAT                13229 18.4%     
 2 RENAULT             12760 17.8%     
 3 FORD                12500 17.4%     
 4 MERCEDES-BENZ        6933 9.7%      
 5 HYUNDAI              5829 8.1%      
 6 DACIA                5492 7.7%      
 7 NISSAN               4429 6.2%      
 8 PEUGEOT              4220 5.9%      
 9 CITROEN              3002 4.2%      
10 KIA                  2789 3.9%      
11 MITSUBISHI            463 0.6%      
12 SSANGYONG              77 0.1%  

##### Also I would like to see a list which total sales is greater than average total sales value in all brands.
```{r}
car_data_nov_17 %>% 
  select(brand_name, auto_total, comm_total, total_total) %>%
  mutate(average_total=mean(total_total)) %>%  
  filter(total_total > average_total)  %>%
  arrange(desc(total_total)) 
```


     
  